The Name of the Title Is Hope

### 2025-01-25 paper.tex
Update dawn. Add Appendix. Add diagnostic ignore for Tint.

\usepackage{amsmath}
\usepackage{mathtools}
\newcommand{\thomas}[1]{{\footnotesize\color{orange}[Thomas: #1]}}
\newcommand{\john}[1]{{\footnotesize\color{cyan}[John: #1]}}
\newcommand{\raph}[1]{{\footnotesize\color{magenta}[Raph: #1]}}

@@

\appendix

\section{Research Methods}

>>>>

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{listings}
\newcommand{\thomas}[1]{{\footnotesize\color{orange}[Thomas: #1]}}
\newcommand{\john}[1]{{\footnotesize\color{cyan}[John: #1]}}
\newcommand{\raph}[1]{{\footnotesize\color{magenta}[Raph: #1]}}

@@

\appendix
\section{Artifact}

\subsection{Availability}
We provide our artifact in the following GitHub repository: 
\thomas{Will anonymize with GithubAnonymous once we are ready.} 
Due to the aforementioned issues with WGSL transpilers, we choose Dawn as our WebGPU implementation.

\subsection{Requirements}

\subsubsection{Device Requirements}
Any device supporting Dawn, with subgroup and timestamp query capabilities, and at least 384 MB of available device memory.

\subsubsection{Software Requirements}
\begin{itemize}
  \item Git
  \item CMake 3.10.2+ or another C++ build tool
  \item C++17-compliant compiler
  \item Python for fetching dependencies
\end{itemize}

\subsection{Building}
Although native WebGPU is supported on various operating systems—most notably Windows, macOS, and Linux—this section will focus on building it in Unix-like environments for the sake of brevity, using CMake as the example build tool.

\subsubsection{Building Dawn}
\begin{enumerate}
  \item[(0)] Dawn depends on the following packages (Ubuntu package names):
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
sudo apt install libxrandr-dev 
  libxinerama-dev libxcursor-dev libxi-dev \
  libx11-xcb-dev mesa-common-dev
  \end{lstlisting}

  \item Clone the Dawn repository:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
git clone https://dawn.googlesource.com/dawn
  \end{lstlisting}

  \item Build and install Dawn with your build tool and compiler of choice:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd dawn
cmake -S . -B out/Release \
  -DDAWN_FETCH_DEPENDENCIES=ON \
  -DDAWN_ENABLE_INSTALL=ON \
  -DCMAKE_BUILD_TYPE=Release
...
cmake --build out/Release
...
cmake --install out/Release \
  --prefix install/Release
  \end{lstlisting}
\end{enumerate}

\subsubsection{Building Artifact}
After successfully building and installing Dawn, follow these steps to build the artifact:

\begin{enumerate}
  \item Navigate to the artifact directory:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd Decoupled-Fallback-Paper/artifact/Dawn
  \end{lstlisting}

  \item Set the `CMAKE\_PREFIX\_PATH` to point to your Dawn installation directory:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
export CMAKE_PREFIX_PATH=/path/to/ \
dawn/install/Release
  \end{lstlisting}

  \item Build the artifact:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake -S . -B out/Release \
  -DCMAKE_BUILD_TYPE=Release
  \end{lstlisting}

  \item Compile the project:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake --build out/Release
  \end{lstlisting}
\end{enumerate}
